\documentclass[letterpaper,10pt]{article}

% ---------- PACKAGES ----------
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[left=0.45in,right=0.45in,top=0.28in,bottom=0.30in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage{microtype}

% ---------- DOCUMENT STYLE ----------
\pagestyle{empty}
\raggedright
\urlstyle{same}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\tabcolsep}{0pt}
\setlength{\emergencystretch}{3em}

% ---------- SECTION STYLE ----------
\titleformat{\section}
  {\large\bfseries}
  {}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{3pt}{1pt}

% ---------- CUSTOM COMMANDS ----------
\newcommand{\resumeSubheading}[4]{
  \begin{tabularx}{\textwidth}{@{}Xr@{}}
    \textbf{#1} & #2 \\
    \textit{\small #3} & \textit{\small #4} \\
  \end{tabularx}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \begin{tabularx}{\textwidth}{@{}Xr@{}}
    \small #1 & \small #2 \\
  \end{tabularx}\vspace{-5pt}
}

\newcommand{\resumeItem}[1]{\item \small{#1}}
\newcommand{\resumeItemListStart}{
  \begin{itemize}[leftmargin=0.18in,label=\textbullet,itemsep=0pt,topsep=1pt,parsep=0pt,partopsep=0pt]
}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

\begin{document}

% ---------- HEADER ----------
\begin{center}
  {\Huge\textbf{Sri Krishna}} \\[2pt]
  {\large\textbf{Machine Learning Engineer $|$ Predictive Modeling \& Time-Series}} \\[4pt]
  \small
  \href{tel:+918409938989}{+91 8409938989} $|$
  \href{mailto:srikrishna11ray@gmail.com}{srikrishna11ray@gmail.com} $|$
  \href{https://resume-hazel-tau-84.vercel.app/}{Portfolio} $|$
  \href{https://www.linkedin.com/in/sri-krishna007/}{LinkedIn} $|$
  \href{https://github.com/Siddhanta007}{GitHub}
\end{center}
\vspace{-7pt}

% ---------- SUMMARY ----------
\section{Professional Summary}
\small{
Machine Learning Engineer with 2 years of experience across industrial predictive modeling, time-series analysis, and production AI systems. Currently responsible for the modeling and analysis of an ESP failure-prediction use case and experienced in gross-margin prediction using operational and market data. Strong foundation in feature engineering, statistical modeling, model evaluation, and applied AI engineering. Currently pursuing the MITx MicroMasters in Statistics and Data Science.
}

% ---------- EXPERIENCE ----------
\section{Experience}

\resumeSubheading
  {Software Engineer -- AI \& Machine Learning}
  {May 2024 -- Present}
  {LTIMindtree}
  {Kolkata, India}

\resumeItemListStart
  \resumeItem{Developing an ESP failure-prediction solution using multivariate operational time-series data, with responsibilities spanning exploratory analysis, feature engineering, model development, validation, and collaboration with data-engineering and client teams.}

  \resumeItem{Built gross-margin prediction workflows using operational and market variables, including preprocessing, statistical feature engineering, model comparison, and evaluation for industrial decision support.}

  \resumeItem{Architected and engineered the Well Agent component within a multi-agent operational intelligence platform, integrating AWS-based speech services, Snowflake-backed data workflows, agent memory, caching, and voice-driven responses for field operators.}

  \resumeItem{Engineered an LLM-powered reverse-engineering workflow that transformed legacy COBOL applications into structured functional documentation for a Tier-1 banking client.}
\resumeItemListEnd

\resumeSubheading
  {Software Engineering Intern -- IGNITE}
  {Aug 2023 -- Oct 2023}
  {LTIMindtree}
  {Remote}

\resumeItemListStart
  \resumeItem{Developed cloud-based machine learning prototypes using AWS services and gained hands-on experience in model deployment, data processing workflows, and enterprise AI application development.}
\resumeItemListEnd

% ---------- PROJECTS ----------
\section{Projects}

\resumeProjectHeading
  {\textbf{TRISHUL -- Regime-Aware Trade Outcome Prediction} $|$ \emph{Python, Scikit-Learn, XGBoost, Time-Series Validation}}
  {In Development}

\resumeItemListStart
  \resumeItem{Building the first module of a quantitative research engine to estimate the probability that predefined NIFTY trading setups reach their target before stop-loss using historical price, volatility, momentum, regime, and time-of-day features.}

  \resumeItem{Implementing leakage-aware event labeling and walk-forward validation to evaluate model performance under changing market conditions rather than random train-test splits.}

  \resumeItem{Comparing interpretable and ensemble classifiers using discrimination, calibration, and feature-attribution analysis, with no performance claims included until validation is complete.}
\resumeItemListEnd

\resumeProjectHeading
  {\textbf{NETRA -- Financial Decision-Intelligence Platform} \href{https://netra-terminal.vercel.app/home}{[Demo]} $|$ \emph{Python, Feature Engineering, GraphRAG, KNN, LLMs}}
  {}

\resumeItemListStart
  \resumeItem{Built a financial decision-support platform by converting discretionary market concepts into structured market-state representations for systematic analysis of context, opportunities, and execution conditions.}

  \resumeItem{Combined engineered market features, historical outcome retrieval, knowledge graphs, and multi-agent reasoning to generate context-aware assessments from live market data.}
\resumeItemListEnd

% ---------- TECHNICAL SKILLS ----------
\section{Technical Skills}
\small{
\textbf{Programming:} Python, SQL \\
\textbf{Machine Learning:} Regression, Classification, Time-Series Forecasting, Feature Engineering, Model Evaluation, Ensemble Methods \\
\textbf{Statistics:} Probability, Statistical Inference, Hypothesis Testing, Time-Series Analysis, Stationarity Testing \\
\textbf{Frameworks:} Scikit-Learn, XGBoost, TensorFlow, NumPy, Pandas, SciPy, Hugging Face \\
\textbf{AI Systems:} Agentic AI, Multi-Agent Systems, RAG, GraphRAG, LangGraph, LangChain, Structured Outputs \\
\textbf{Cloud \& Data:} AWS Bedrock, Bedrock AgentCore, Lambda, EKS, SageMaker, S3, Snowflake, Palantir, Docker, Git
}

% ---------- EDUCATION ----------
\section{Education}

\resumeSubheading
  {Massachusetts Institute of Technology (MITx)}
  {Jan 2026 -- Present}
  {MicroMasters Program in Statistics and Data Science -- Methods Track}
  {Remote}

\resumeSubheading
  {St. Thomas' College of Engineering and Technology}
  {Aug 2019 -- May 2023}
  {B.Tech in Information Technology -- CGPA: 9.10/10}
  {Kolkata, India}

% ---------- ACHIEVEMENTS ----------
\section{Achievements \& Certifications}
\resumeItemListStart
  \resumeItem{\textbf{Enterprise AI Recognition:} Contributed to an AI-powered operational intelligence platform featured in the \textit{Wall Street Journal}; received the \textbf{LTIM Energy Portfolio Innovators Award}.}
  \resumeItem{\textbf{Machine Learning:} Selected for the \textbf{Amazon ML Summer School}, completing advanced training in deep learning, probabilistic graphical models, causal inference, and reinforcement learning.}
  \resumeItem{\textbf{Competitive Programming:} Global Rank 19 in the CodeChef November Cook-Off among 6,000+ participants; solved 1,000+ DSA problems.}
  \resumeItem{\textbf{Certification:} GitHub Copilot Certified.}
\resumeItemListEnd

\end{document}
